---
title: "Assignment 4"
author: "Kazia Mermel"
date: "5/24/2020"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

# Variables:
# temperature at time t
# t = time
# t_diff = T = temperature at time 100 (given)

 #overall value for T

# Givens & Vectors:

t_vector <- seq(0,200, by = 1)

```


Structure for Functions 1 - 5 is next.

```{r}
# Function 1 - Temperature(t)

temp <- function(t, t_diff){
  out = pmin((t*t_diff)/100,t_diff)
  return(out)
}


# Function 2 - Retention (t)

retention <- function(t, t_diff, B){
  out = exp(-B * (temp(t, t_diff))^2)
  return(out)
}


# Function 3 - Consumption (t)
consumption <- function(t, t_diff, B, g){
  out = retention(t, t_diff, B) * exp(g*t)
  return(out)
}


# Function 4 - Utility (C)

utility <- function(C, n){
  out = (C^(1-n))/(1-n)
  return(out)
}


# Function 5 - Discount Rate (Ramsey Rule)

r <- function(d, n, g){
  out = (d + n*g)
  return(out)
}


```


*Data Frames for Plots*

Givens for Part 1

t_diff = 5 # T
B = .05
g = .01
n = .5
d = .005   # delta

*T = 0*

```{r}
# T = 0

# Temperature df

temp_df_T_0 <- data.frame(t = t_vector) %>% 
  mutate(temp = temp(t_vector,
                     t_diff = 0))
  

# Retention df

retent_df_T_0 <- data.frame(t = t_vector) %>% 
  mutate(retent = retention(t_vector,
                            t_diff = 0,
                            B = .05)) 
# Consumption df

consum_df_T_0 <- data.frame(t = t_vector) %>% 
  mutate(consum = consumption(t_vector,
                              t_diff = 0,
                              B = 0.05,
                              g = 0.01))

# Utility df

C_0 <- consum_df_T_0$consum

utility_df_T_0 <- data.frame(t = t_vector) %>% 
  mutate(consum = C_0) %>% 
  mutate(utility = utility(C = C_0,
                           n = .5))
  
```

*T = 2*

```{r}
# T = 2

# Temperature df

temp_df_T_2 <- data.frame(t = t_vector) %>% 
  mutate(temp = temp(t_vector,
                     t_diff = 2)) 

# Retention df

retent_df_T_2 <- data.frame(t = t_vector) %>% 
  mutate(retent = retention(t_vector,
                            t_diff = 2,
                            B = .05)) 
# Consumption df

consum_df_T_2 <- data.frame(t = t_vector) %>% 
  mutate(consum = consumption(t_vector,
                              t_diff = 2,
                              B = 0.05,
                              g = 0.01))

# Utility df

C_2 <- consum_df_T_2$consum

utility_df_T_2 <- data.frame(t = t_vector) %>% 
  mutate(consum = C_2) %>% 
  mutate(utility = utility(C = C_2,
                           n = .5))
  
```

*T = 8*
```{r}
# T = 8

# Temperature df

temp_df_T_8 <- data.frame(t = t_vector) %>% 
  mutate(temp = temp(t_vector,
                     t_diff = 8))

# Retention df

retent_df_T_8 <- data.frame(t = t_vector) %>% 
  mutate(retent = retention(t_vector,
                            t_diff = 8,
                            B = .05)) 
# Consumption df

consum_df_T_8 <- data.frame(t = t_vector) %>% 
  mutate(consum = consumption(t_vector,
                              t_diff = 8,
                              B = 0.05,
                              g = 0.01))

# Utility df

C_8 <- consum_df_T_8$consum

utility_df_T_8 <- data.frame(t = t_vector) %>% 
  mutate(consum = C_8) %>% 
  mutate(utility = utility(C = C_8,
                           n = .5))
  
```

Question 1
```{r}
# a
# plot temperature over time
# scenario 1: no climate change


# scenario 2: moderate climate change

# scenario 3: major climate change
```


Plot 1a
```{r}
ggplot () +
  geom_line(data = temp_df_T_0,
            aes( x = t,
                 y = temp),
            size = 1.5,
            color = "blue") +
  geom_line(data = temp_df_T_2,
            aes( x = t,
                 y = temp),
            size = 1.5,
            color = "green") +
  geom_line(data = temp_df_T_8,
            aes( x = t,
                 y = temp),
            size = 1.5,
            color = "red") +
  labs(title = "Predictions of Temperature Increase Due to Climate Change" ,
       x = "Time (years)",
       y = "Temperature Increase Relative to Present (degrees)",
       caption = "Figure 1") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0),
        axis.title.y = element_text(size = 10))
             
```
Figure 1 (above) plots estimated temperature change over time for three possible climate scenarios. In order from bottom to top we have temperature changes over time for: no climate change (blue), modest climate change (green), and extreme climate change (red).

Plot 1b
```{r}
ggplot () +
  geom_line(data = consum_df_T_0,
             aes( x = t,
                  y = consum),
             size = 1.5,
             color = "blue") +
  geom_line(data = consum_df_T_2,
             aes( x = t,
                  y = consum),
             size = 1.5,
             color = "green") +
  geom_line(data = consum_df_T_8,
             aes( x = t,
                  y = consum),
             size = 1.5,
             color = "red") +
  labs(title = "Climate Change's Effect on Consumption Over Time" ,
       x = "Time (years)",
       y = "Consumption (dollars)",
       caption = "Figure 2") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0),
        axis.title.y = element_text(size = 10))
```
Figure 2 (above) plots economic activity (consumption) change over time for three possible climate scenarios. In order from bottom to top we have temperature changes over time for: extreme climate change (red), modest climate change (green), and no climate change (blue).



```{r}
ggplot () +
  geom_line(data = utility_df_T_0,
            aes( x = t,
                  y = utility),
            size = 1.5,
            color = "blue") +
  geom_line(data = utility_df_T_2,
            aes( x = t,
                  y = utility),
            size = 1.5,
            color = "green") +
  geom_line(data = utility_df_T_8,
            aes( x = t,
                  y = utility),
            size = 1.5,
            color = "red") +
labs(title = "Climate Change's Effect on Discounted Utility Over Time" ,
       x = "Time (years)",
       y = "Discounted Utility (dollars)",
       caption = "Figure 3") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0),
        axis.title.y = element_text(size = 10))
```
Figure 3 (above) plots estimated changes in discounted societal utility over time for three possible climate scenarios. In order from bottom to top we have temperature changes over time for: extreme climate change (red), modest climate change (green), and no climate change (blue).



**Question 2a**

*T = 4.4*
```{r}
# T = 4.4
# Maintained givens from plot 1

# Temperature df

temp_df_T_4_4 <- data.frame(t = t_vector) %>% 
  mutate(temp = temp(t_vector,
                     t_diff = 4.4))

# Retention df

retent_df_T_4_4 <- data.frame(t = t_vector) %>% 
  mutate(retent = retention(t_vector,
                            t_diff = 4.4,
                            B = .05)) 
# Consumption df

consum_df_T_4_4 <- data.frame(t = t_vector) %>% 
  mutate(consum = consumption(t_vector,
                              t_diff = 4.4,
                              B = 0.05,
                              g = 0.01))

# Utility df

C_4_4 <- consum_df_T_4_4$consum

utility_df_T_4_4 <- data.frame(t = t_vector) %>% 
  mutate(consum = C_4_4) %>% 
  mutate(utility = utility(C = C_4_4,
                           n = .5))
  
```


Present value discounted over 200 years w/ & w/o climate change

```{r}
# Present value discounted over 200 years w/ climate change

# discount rate
r_given <- r(.005, .5, .01)

# Value calculation
pv_df_4_4 <- data.frame(t = t_vector) %>% 
  mutate(pv_4_4 = (utility_df_T_4_4$utility)/(1 + r_given)^(t_vector))

pv_4_4 = sum(pv_df_4_4$pv_4_4)

# Present value discounted over 200 years w/o climate change

# Value calculation
pv_df_0 <- data.frame(t = t_vector) %>% 
  mutate(pv_0 = (utility_df_T_0$utility)/(1 + r_given)^(t_vector))

pv_0 = sum(pv_df_0$pv_0)
```

Percentage Loss (L)
```{r}

L_cc <- abs(pv_0-pv_4_4)/pv_0 * 100


```

The present value (i.e. discounted) utility over the next 200 years without climate change is estimated to be $255.27. With an increase in temperature of 4.4 degrees over the next 200 years is estimated to be $198.66. There is a 22.177% loss in utility between the 4.4 degree increase and the busiess as usual scenario. 

**Question 2b**

Sensitivity of T
```{r}
# Present value discounted over 200 years w/ climate change
# T = 4.4 + .44 = 4.84

# Temperature df

temp_df_T_4_84 <- data.frame(t = t_vector) %>% 
  mutate(temp = temp(t_vector,
                     t_diff = 4.84))

# Retention df

retent_df_T_4_84 <- data.frame(t = t_vector) %>% 
  mutate(retent = retention(t_vector,
                            t_diff = 4.84,
                            B = .05)) 
# Consumption df

consum_df_T_4_84 <- data.frame(t = t_vector) %>% 
  mutate(consum = consumption(t_vector,
                              t_diff = 4.84,
                              B = 0.05,
                              g = 0.01))

# Utility df

C_4_84 <- consum_df_T_4_84$consum

utility_df_T_4_84 <- data.frame(t = t_vector) %>% 
  mutate(consum = C_4_84) %>% 
  mutate(utility = utility(C = C_4_84,
                           n = .5))

# Value calculation
pv_df_4_84 <- data.frame(t = t_vector) %>% 
  mutate(pv_4_84 = (utility_df_T_4_84$utility)/(1 + r_given)^(t_vector))

pv_4_84 = sum(pv_df_4_84$pv_4_84)

```

Percentage Loss (L) for T Sensitivy Analysis
```{r}

L_T_sens <- abs(pv_0-pv_4_84)/pv_0 * 100


```


Sensitivity of B
```{r}
# T = 4.4 ************************************************************************************************
# B = .055

# Retention df

retent_df_B_055 <- data.frame(t = t_vector) %>% 
  mutate(retent = retention(t_vector,
                            t_diff = 4.4,
                            B = .055)) 
# Consumption df

consum_df_B_055 <- data.frame(t = t_vector) %>% 
  mutate(consum = consumption(t_vector,
                              t_diff = 4.4,
                              B = 0.055,
                              g = 0.01))

# Utility df

C_B_055 <- consum_df_B_055$consum

utility_df_B_055 <- data.frame(t = t_vector) %>% 
  mutate(consum = C_B_055) %>% 
  mutate(utility = utility(C = C_B_055,
                           n = .5))

# Value calculation
pv_df_B_055 <- data.frame(t = t_vector) %>% 
  mutate(pv_B_055 = (utility_df_B_055$utility)/(1 + r_given)^(t_vector))

pv_B_055 = sum(pv_df_B_055$pv_B_055)

# T = 0 *************************************************************************************************
# B = .055

# Retention df

retent_df_T_0_B <- data.frame(t = t_vector) %>% 
  mutate(retent = retention(t_vector,
                            t_diff = 0,
                            B = .055)) 
# Consumption df

consum_df_T_0_B <- data.frame(t = t_vector) %>% 
  mutate(consum = consumption(t_vector,
                              t_diff = 0,
                              B = 0.055,
                              g = 0.01))

# Utility df

C_0_B <- consum_df_T_0_B$consum

utility_df_T_0_B <- data.frame(t = t_vector) %>% 
  mutate(consum = C_0_B) %>% 
  mutate(utility = utility(C = C_0_B,
                           n = .5))

# Present value discounted over 200 years w/o climate change
# Value calculation
pv_df_0_B <- data.frame(t = t_vector) %>% 
  mutate(pv_0_B = (utility_df_T_0_B$utility)/(1 + r_given)^(t_vector))

pv_0_B = sum(pv_df_0_B$pv_0_B)
```


Percentage Loss (L) for B Sensitivy Analysis
```{r}

L_B_sens <- abs(pv_0_B-pv_B_055)/pv_0_B * 100


```


Sensitivity of g
```{r}
# T = 4.4 ***********************************************************************
# g = .01 + .001 = .011

# Consumption df

consum_df_g_01 <- data.frame(t = t_vector) %>% 
  mutate(consum = consumption(t_vector,
                              t_diff = 4.4,
                              B = 0.05,
                              g = 0.011))

# Utility df

C_g_01 <- consum_df_g_01$consum

utility_df_g_01 <- data.frame(t = t_vector) %>% 
  mutate(consum = C_g_01) %>% 
  mutate(utility = utility(C = C_g_01,
                           n = .5))

#T = 0****************************************************************************
# g = .01 + .001 = .011
# Temperature df

# Consumption df

consum_df_T_0_g <- data.frame(t = t_vector) %>% 
  mutate(consum = consumption(t_vector,
                              t_diff = 0,
                              B = 0.05,
                              g = 0.011))

# Utility df

C_0_g <- consum_df_T_0_g$consum

utility_df_T_0_g <- data.frame(t = t_vector) %>% 
  mutate(consum = C_0_g) %>% 
  mutate(utility = utility(C = C_0_g,
                           n = .5))


# discount rate
r_g <- r(.005, .5, .011) 

# Value calculation
pv_df_g_01 <- data.frame(t = t_vector) %>% 
  mutate(pv_g_01 = (utility_df_g_01$utility)/(1 + r_g)^(t_vector))

pv_g_01 = sum(pv_df_g_01$pv_g_01)

# Present value discounted over 200 years w/o climate change

# Value calculation
pv_df_0_g <- data.frame(t = t_vector) %>% 
  mutate(pv_0_g = (utility_df_T_0_g$utility)/(1 + r_g)^(t_vector))

pv_0_g = sum(pv_df_0_g$pv_0_g)
```


Percentage Loss (L) for g Sensitivy Analysis
```{r}

L_g_sens <- abs(pv_0_g-pv_g_01)/pv_0_g * 100


```


Sensitivity of n
```{r}
# T = 4.4************************************************************************
# n = 0.5 +.05 = 0.55


# Utility df
# C_4_4 is not affected by N so it is ok to leave as is

utility_df_n_55 <- data.frame(t = t_vector) %>% 
  mutate(consum = C_4_4) %>% 
  mutate(utility = utility(C = C_4_4,
                           n = .55))

# T = 0 ************************************************************************
# n = 0.5 +.05 = 0.55

# Utility df
# Leave consum = C_0 because it is unaffected by n

utility_df_T_0_n <- data.frame(t = t_vector) %>% 
  mutate(consum = C_0) %>% 
  mutate(utility = utility(C = C_0,
                           n = .55))

# discount rate
r_n <- r(.005, .55, .01) 

# Value calculation
pv_df_n_55 <- data.frame(t = t_vector) %>% 
  mutate(pv_n_55 = (utility_df_n_55$utility)/(1 + r_n)^(t_vector))

pv_n_55 = sum(pv_df_n_55$pv_n_55)

# Present value discounted over 200 years w/o climate change

# Value calculation
pv_df_0_n <- data.frame(t = t_vector) %>% 
  mutate(pv_0_n = (utility_df_T_0_n$utility)/(1 + r_n)^(t_vector))

pv_0_n = sum(pv_df_0_n$pv_0_n)
```


Percentage Loss (L) for n Sensitivy Analysis
```{r}

L_n_sens <- abs(pv_0_n-pv_n_55)/pv_0_n * 100


```

Our calculation of L in 2a is not overly sensitive to different changes in specific parameters. With a 10% increase in T, g, n, and B, there are associated changes of 3.62%, 0.4%, 2.581%, and 1.762% compared the original L we calculated. Given this information, it is safe to assume that our climate-economy model is fairly robust to possible error. 

**Question 2c**

Givens:
Vnot = p_4_4
Vsubt = utility(C) for T = 0 = utility_df_T_0
d = 0.005
n = 0.5
g = 0.01
B = 0.05

```{r}
# Made the below function to populate values to a data frame for values of theta from 0 - 1. pv_theta is eqiuvalent to the present value at each one of those thetas.
# To match pv_4_4 = 198.66 we have to find the pv_theta value that matches 198.66. It is around 40%

#Givens:
theta_vector <- seq(0,1,by = .005)
n = 0.5

theta_solver_pv_0 <- function(theta) { 
  out = (1-theta)^(1-n)*pv_0
  return(out)
  
pv_theta_T_4_4 <- data.frame(t = t_vector)  %>% 
  mutate(theta = theta_vector) %>% 
  mutate( pv_theta = theta_solver_pv_0(theta_vector))
}


```


Answer = line 80is,  approx 40% (39.5)

The maximum fractional value of consumption society would be willing to endure every year to completely prevent climate change (from a 4.4 degree increase) is equal to approximately 40% of consumption every year.

**Question 2d**

Before solving for theta star we need to calculate utility_df_T_4, utility_df_T_6, pv_2, pv_4, pv_6.

```{r}
#pv_2

pv_df_2 <- data.frame(t = t_vector) %>% 
  mutate(pv_2 = (utility_df_T_2$utility)/(1 + r_given)^(t_vector))

pv_2 = sum(pv_df_2$pv_2)

```
```{r}
# T = 4

# Temperature df

temp_df_T_4 <- data.frame(t = t_vector) %>% 
  mutate(temp = temp(t_vector,
                     t_diff = 4)) 

# Retention df

retent_df_T_4 <- data.frame(t = t_vector) %>% 
  mutate(retent = retention(t_vector,
                            t_diff = 4,
                            B = .05)) 
# Consumption df

consum_df_T_4 <- data.frame(t = t_vector) %>% 
  mutate(consum = consumption(t_vector,
                              t_diff = 4,
                              B = 0.05,
                              g = 0.01))

# Utility df

C_4 <- consum_df_T_4$consum

utility_df_T_4 <- data.frame(t = t_vector) %>% 
  mutate(consum = C_4) %>% 
  mutate(utility = utility(C = C_4,
                           n = .5))
```
```{r}
#pv_4

pv_df_4 <- data.frame(t = t_vector) %>% 
  mutate(pv_4 = (utility_df_T_4$utility)/(1 + r_given)^(t_vector))

pv_4 = sum(pv_df_4$pv_4)

```

```{r}
# T = 6

# Temperature df

temp_df_T_6 <- data.frame(t = t_vector) %>% 
  mutate(temp = temp(t_vector,
                     t_diff = 6)) 

# Retention df

retent_df_T_6 <- data.frame(t = t_vector) %>% 
  mutate(retent = retention(t_vector,
                            t_diff = 6,
                            B = .05)) 
# Consumption df

consum_df_T_6 <- data.frame(t = t_vector) %>% 
  mutate(consum = consumption(t_vector,
                              t_diff = 6,
                              B = 0.05,
                              g = 0.01))

# Utility df

C_6 <- consum_df_T_6$consum

utility_df_T_6 <- data.frame(t = t_vector) %>% 
  mutate(consum = C_6) %>% 
  mutate(utility = utility(C = C_6,
                           n = .5))
```


```{r}
#pv_6

pv_df_6 <- data.frame(t = t_vector) %>% 
  mutate(pv_6 = (utility_df_T_6$utility)/(1 + r_given)^(t_vector))

pv_6 = sum(pv_df_6$pv_6)
```


```{r}

theta_solver_prob <- function(theta) { 
  out = (1-theta)^(1-n)*((pv_2*0.2)+(pv_4*0.5) + (pv_6*0.3))
  return(out)
}
  
pv_theta_T_prob <- data.frame(t = t_vector)  %>% 
  mutate(theta = theta_vector) %>% 
  mutate( pv_theta = theta_solver_prob(theta_vector))


```


0.025 = 1/40 = 2.5%

Under uncertainty, the maximum fractional value of consumption society would be willing to endure every year to completely prevent climate change is equal to approximately ... having trouble finding it tbh...unsure why 

































